---
title: <font size = "5"> Summary figures for all SOM event yield results </font>
author: "Dustin Kincaid"
date: "04/21/2021<br><br>"
output: html_document
editor_options: 
  chunk_output_type: console
---

### Objective  
##### Create key figures for paper summarizing all results of SOM clustered flux regimes on event water, NO3, SRP, and turbidity yields from Hungerford and Wade Brooks
<br><br>

```{r setup, include=FALSE, warning=FALSE, message = FALSE}
# Set defaults
knitr::opts_chunk$set(fig.width = 6, fig.asp = 0.618, out.width = "70%", fig.align = "center")

# Load packages
  library("here")      # to make file paths fail less
  library("tidyverse") # general workhorse
  library("lubridate") # to work with dates
  library("patchwork") # arranging multiple plots
  library("broom")     # for linear regressions
```

```{r data, include=FALSE, warning=FALSE, message = FALSE}
# Read in data
  # Calculated event metrics for each site as calculated in compile_calculate_allVars.R
  hford <- read_csv(here("Data", "eventMetrics_hford.csv")) %>% 
    mutate(event_start = ymd_hms(event_start, tz = "Etc/GMT+4"))

  wade <- read_csv(here("Data", "eventMetrics_wade.csv")) %>% 
    mutate(event_start = ymd_hms(event_start, tz = "Etc/GMT+4"))

  # SOM results from SOManalysis_SITE_yields_VAR.Rmd
  # Water
  som_wat_hf <- read_csv(here("Data", "somResults", "hford", "yields", "water", "2021-04-07", "Results_hford_withClusters.csv")) %>% mutate(SOM = "water") %>% select(site, SOM, everything())
  som_wat_wd <- read_csv(here("Data", "somResults", "wade", "yields", "water", "2021-04-07", "Results_wade_withClusters.csv")) %>% mutate(SOM = "water") %>% select(site, SOM, everything())
  # NO3
  som_no3_hf <- read_csv(here("Data", "somResults", "hford", "yields", "NO3", "2021-04-08", "Results_hford_withClusters.csv")) %>% mutate(SOM = "NO3_kg_km2") %>% select(site, SOM, everything())
  som_no3_wd <- read_csv(here("Data", "somResults", "wade", "yields", "NO3", "2021-04-12", "Results_wade_withClusters.csv")) %>% mutate(SOM = "NO3_kg_km2") %>% select(site, SOM, everything())
  # SRP
  som_srp_hf <- read_csv(here("Data", "somResults", "hford", "yields", "SRP", "2021-04-08", "Results_hford_withClusters.csv")) %>% mutate(SOM = "SRP_kg_km2") %>% select(site, SOM, everything())
  som_srp_wd <- read_csv(here("Data", "somResults", "wade", "yields", "SRP", "2021-04-12", "Results_wade_withClusters.csv")) %>% mutate(SOM = "SRP_kg_km2") %>% select(site, SOM, everything())
  # Turbidity
  som_turb_hf <- read_csv(here("Data", "somResults", "hford", "yields", "turb", "2021-04-09", "Results_hford_withClusters.csv")) %>% mutate(SOM = "turb_kg_km2") %>% select(site, SOM, everything())
  som_turb_wd <- read_csv(here("Data", "somResults", "wade", "yields", "turb", "2021-04-13", "Results_wade_withClusters.csv")) %>% mutate(SOM = "turb_kg_km2") %>% select(site, SOM, everything())
  
# Join SOM results into one df per site
  som_results <- bind_rows(som_wat_hf, som_wat_wd, som_no3_hf, som_no3_wd, som_srp_hf, som_srp_wd, som_turb_hf, som_turb_wd) %>% 
    rename(clust_4cl = clust_wat_4cl, clust_5cl = clust_wat_5cl, clust_6cl = clust_wat_6cl) %>% 
    mutate(event_start = ymd_hms(event_start, tz = "Etc/GMT+4"))
  rm(som_wat_hf, som_wat_wd, som_no3_hf, som_no3_wd, som_srp_hf, som_srp_wd, som_turb_hf, som_turb_wd)
```

```{r plot themes and labels, include = FALSE}
# Plotting specifics
  theme1 <- theme_classic() +
            theme(axis.text = element_text(size = 11),
                  axis.title = element_text(size = 12),
                  axis.title.x = element_text(margin=margin(5,0,0,0)),
                  axis.title.y = element_text(margin=margin(0,5,0,0)),
                  legend.title = element_text(size = 9),
                  legend.text = element_text(size = 9),
                  strip.text = element_text(size = 12))
  
  # A new theme for the hysteresis plots
  theme2 <- theme(axis.line = element_blank(),
                  axis.text = element_text(size = 8),
                  axis.title = element_blank(),
                  plot.margin = unit(c(1.25,1.25,1.25,1.25), "lines"),
                  panel.background = element_blank(),
                  panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank(),
                  legend.text = element_text(size = 6),
                  legend.key.size = unit(0.1, "in"),
                  legend.margin = margin(0, 0, 0, 0),
                  legend.title = element_text(size = 6)) 
```

##### Ice-free season yields attributed to each cluster
```{r h2o prop, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.asp = .9, out.width = "80%"}
# Plot total yield attributed to each cluster
# HFORD
  # Calculate annual measured event yields
  annYields <-
    som_results %>%
    # Calculate the cummulative sum of yields for each solute, year, and cluster #
    mutate(year = year(event_start)) %>% 
    group_by(year) %>% 
    summarize(ann_NO3_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup()

  # Stacked bar graph (year on x-axis; stacks = yields by cluster)
  # Total event water yield per category
  # 4 clusters
  p_hf_8 <- som_hf %>%
    # Calculate the cummulative sum of yields for each year and cluster #
    mutate(year = year(event_start)) %>% 
    group_by(year, clust_wat_4cl) %>% 
    summarize(tot_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup() %>% 
    # Exclude 2017 events  
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(year), y = tot_yield, fill = factor(clust_wat_4cl))) +
      geom_bar(position = "stack", stat = "identity") +
      scale_fill_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(atop(Event~NO[3]^-{}~yield, "during ice-free season"))) +
      xlab("Year") +
      theme1 +
      theme(legend.position = "none",
            axis.text.x = element_blank(),
            axis.title.x = element_blank()) +
      ggtitle("4 cl. model")
  
  # 5 clusters
  p_hf_9 <- som_hf %>%
    # Calculate the cummulative sum of yields for each year and cluster #
    mutate(year = year(event_start)) %>% 
    group_by(year, clust_wat_5cl) %>% 
    summarize(tot_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup() %>% 
    # Exclude 2017 events  
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(year), y = tot_yield, fill = factor(clust_wat_5cl))) +
      geom_bar(position = "stack", stat = "identity") +
      scale_fill_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(atop(Event~NO[3]^-{}~yield, "during ice-free season"))) +
      xlab("Year") +
      theme1 +
      theme(legend.position = "none",
            axis.text.x = element_blank(),
            axis.title.x = element_blank()) +
      ggtitle("5 cl. model") 
  
  # 6 clusters
  # NOTE: Colors are rearranged here to make clusters align with above 2 models; if anything changes, change these
  p_hf_10 <- som_hf %>%
    # Calculate the cummulative sum of yields for each year and cluster #
    mutate(year = year(event_start)) %>% 
    group_by(year, clust_wat_6cl) %>% 
    summarize(tot_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup() %>% 
    # Exclude 2017 events  
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(year), y = tot_yield, fill = factor(clust_wat_6cl))) +
      geom_bar(position = "stack", stat = "identity") +
      scale_fill_manual(name = "Cluster",
                        # These have been rearranged for this model
                        values = c("#0072B2", "#009E73", "#E69F00", "#D55E00", "#56B4E9", "#999999", "#CC79A7")) +
      ylab(expression(atop(Event~NO[3]^-{}~yield, "during ice-free season"))) +
      xlab("Year") +
      theme1 +
      theme(legend.position = "none") +
      ggtitle("6 cl. model")    

  # % of event water yield during ice-free season
  # 4 clusters
  p_hf_11 <- som_hf %>%
    # Calculate the cummulative sum of yields for each solute, year, and cluster #
    mutate(year = year(event_start)) %>% 
    # pivot_longer(cols = c(NO3_kg_km2, SRP_kg_km2), names_to = "var", values_to = "value") %>% 
    # group_by(year, cluster, var) %>% 
    group_by(year, clust_wat_4cl) %>% 
    summarize(tot_NO3_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup() %>% 
    # Calculate proportion of total annual yield
    full_join(annYields) %>% 
    mutate(prop_NO3_yield = tot_NO3_yield/ann_NO3_yield) %>% 
    # Exclude 2017 events
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(year), y = prop_NO3_yield*100, fill = factor(clust_wat_4cl))) +
      # facet_wrap(~var, ncol = 2, scales = "free_y", labeller = labeller(var = labels_var)) +
      geom_bar(position = "stack", stat = "identity") +
      # scale_fill_manual(name = "Cluster",
      #                   values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7"),
      #                   labels = c("Warm, dry soil, big rain", 
      #                              "Very wet soil, rain/melt",
      #                              "Cold, dry soil, mostly melt",
      #                              "Low sun, wet soil, low-int. rain")) +
      scale_fill_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(atop('%'~event~NO[3]^-{}~yield, "during ice-free season"))) +
      xlab("Year") +
      theme1 +
      theme(axis.text.x = element_blank(),
            axis.title.x = element_blank())
  
  # 5 clusters
  p_hf_12 <- som_hf %>%
    # Calculate the cummulative sum of yields for each solute, year, and cluster #
    mutate(year = year(event_start)) %>% 
    # pivot_longer(cols = c(NO3_kg_km2, SRP_kg_km2), names_to = "var", values_to = "value") %>% 
    # group_by(year, cluster, var) %>% 
    group_by(year, clust_wat_5cl) %>% 
    summarize(tot_NO3_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup() %>% 
    # Calculate proportion of total annual yield
    full_join(annYields) %>% 
    mutate(prop_NO3_yield = tot_NO3_yield/ann_NO3_yield) %>% 
    # Exclude 2017 events
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(year), y = prop_NO3_yield*100, fill = factor(clust_wat_5cl))) +
      # facet_wrap(~var, ncol = 2, scales = "free_y", labeller = labeller(var = labels_var)) +
      geom_bar(position = "stack", stat = "identity") +
      # scale_fill_manual(name = "Cluster",
      #                   values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7"),
      #                   labels = c("Warm, dry soil, big rain", 
      #                              "Very wet soil, rain/melt",
      #                              "Cold, dry soil, mostly melt",
      #                              "Low sun, wet soil, low-int. rain")) +
      scale_fill_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(atop('%'~event~NO[3]^-{}~yield, "during ice-free season"))) +
      xlab("Year") +
      theme1 +
      theme(axis.text.x = element_blank(),
            axis.title.x = element_blank())
  
  # 6 clusters
  # NOTE: Colors are rearranged here to make clusters align with above 2 models; if anything changes, change these
  p_hf_13 <- som_hf %>%
    # Calculate the cummulative sum of yields for each solute, year, and cluster #
    mutate(year = year(event_start)) %>% 
    # pivot_longer(cols = c(NO3_kg_km2, SRP_kg_km2), names_to = "var", values_to = "value") %>% 
    # group_by(year, cluster, var) %>% 
    group_by(year, clust_wat_6cl) %>% 
    summarize(tot_NO3_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup() %>% 
    # Calculate proportion of total annual yield
    full_join(annYields) %>% 
    mutate(prop_NO3_yield = tot_NO3_yield/ann_NO3_yield) %>% 
    # Exclude 2017 events
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(year), y = prop_NO3_yield*100, fill = factor(clust_wat_6cl))) +
      # facet_wrap(~var, ncol = 2, scales = "free_y", labeller = labeller(var = labels_var)) +
      geom_bar(position = "stack", stat = "identity") +
      # scale_fill_manual(name = "Cluster",
      #                   values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7"),
      #                   labels = c("Warm, dry soil, big rain", 
      #                              "Very wet soil, rain/melt",
      #                              "Cold, dry soil, mostly melt",
      #                              "Low sun, wet soil, low-int. rain")) +
      scale_fill_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(atop('%'~event~NO[3]^-{}~yield, "during ice-free season"))) +
      xlab("Year") +
      theme1  
  
  # Combine into one plot
  (p_hf_8 + p_hf_11) / (p_hf_9 + p_hf_12) / (p_hf_10 + p_hf_13) +
    plot_annotation(
      title = "Hungerford"
    )
  
# WADE
  # Calculate annual measured event yields
  annYields <-
    som_wd %>%
    # Calculate the cummulative sum of yields for each solute, year, and cluster #
    mutate(year = year(event_start)) %>% 
    group_by(year) %>% 
    summarize(ann_NO3_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup()

  # Stacked bar graph (year on x-axis; stacks = yields by cluster)
  # Total event water yield per category
  # 4 clusters
  p_wd_8 <- som_wd %>%
    # Calculate the cummulative sum of yields for each year and cluster #
    mutate(year = year(event_start)) %>% 
    group_by(year, clust_wat_4cl) %>% 
    summarize(tot_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup() %>% 
    # Exclude 2017 events  
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(year), y = tot_yield, fill = factor(clust_wat_4cl))) +
      geom_bar(position = "stack", stat = "identity") +
      scale_fill_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(atop(Event~NO[3]^-{}~yield, "during ice-free season"))) +
      xlab("Year") +
      theme1 +
      theme(legend.position = "none",
            axis.text.x = element_blank(),
            axis.title.x = element_blank()) +
      ggtitle("4 cl. model")
  
  # 5 clusters
  p_wd_9 <- som_wd %>%
    # Calculate the cummulative sum of yields for each year and cluster #
    mutate(year = year(event_start)) %>% 
    group_by(year, clust_wat_5cl) %>% 
    summarize(tot_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup() %>% 
    # Exclude 2017 events  
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(year), y = tot_yield, fill = factor(clust_wat_5cl))) +
      geom_bar(position = "stack", stat = "identity") +
      scale_fill_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(atop(Event~NO[3]^-{}~yield, "during ice-free season"))) +
      xlab("Year") +
      theme1 +
      theme(legend.position = "none",
            axis.text.x = element_blank(),
            axis.title.x = element_blank()) +
      ggtitle("5 cl. model") 
  
  # 6 clusters
  # NOTE: Colors are rearranged here to make clusters align with above 2 models; if anything changes, change these
  p_wd_10 <- som_wd %>%
    # Calculate the cummulative sum of yields for each year and cluster #
    mutate(year = year(event_start)) %>% 
    group_by(year, clust_wat_6cl) %>% 
    summarize(tot_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup() %>% 
    # Exclude 2017 events  
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(year), y = tot_yield, fill = factor(clust_wat_6cl))) +
      geom_bar(position = "stack", stat = "identity") +
      scale_fill_manual(name = "Cluster",
                        # These have been rearranged for this model
                        values = c("#0072B2", "#009E73", "#E69F00", "#D55E00", "#56B4E9", "#999999", "#CC79A7")) +
      ylab(expression(atop(Event~NO[3]^-{}~yield, "during ice-free season"))) +
      xlab("Year") +
      theme1 +
      theme(legend.position = "none") +
      ggtitle("6 cl. model")    

  # % of event water yield during ice-free season
  # 4 clusters
  p_wd_11 <- som_wd %>%
    # Calculate the cummulative sum of yields for each solute, year, and cluster #
    mutate(year = year(event_start)) %>% 
    # pivot_longer(cols = c(NO3_kg_km2, SRP_kg_km2), names_to = "var", values_to = "value") %>% 
    # group_by(year, cluster, var) %>% 
    group_by(year, clust_wat_4cl) %>% 
    summarize(tot_NO3_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup() %>% 
    # Calculate proportion of total annual yield
    full_join(annYields) %>% 
    mutate(prop_NO3_yield = tot_NO3_yield/ann_NO3_yield) %>% 
    # Exclude 2017 events
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(year), y = prop_NO3_yield*100, fill = factor(clust_wat_4cl))) +
      # facet_wrap(~var, ncol = 2, scales = "free_y", labeller = labeller(var = labels_var)) +
      geom_bar(position = "stack", stat = "identity") +
      # scale_fill_manual(name = "Cluster",
      #                   values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7"),
      #                   labels = c("Warm, dry soil, big rain", 
      #                              "Very wet soil, rain/melt",
      #                              "Cold, dry soil, mostly melt",
      #                              "Low sun, wet soil, low-int. rain")) +
      scale_fill_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(atop('%'~event~NO[3]^-{}~yield, "during ice-free season"))) +
      xlab("Year") +
      theme1 +
      theme(axis.text.x = element_blank(),
            axis.title.x = element_blank())
  
  # 5 clusters
  p_wd_12 <- som_wd %>% 
    # Calculate the cummulative sum of yields for each solute, year, and cluster #
    mutate(year = year(event_start)) %>% 
    # pivot_longer(cols = c(NO3_kg_km2, SRP_kg_km2), names_to = "var", values_to = "value") %>% 
    # group_by(year, cluster, var) %>% 
    group_by(year, clust_wat_5cl) %>% 
    summarize(tot_NO3_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup() %>% 
    # Calculate proportion of total annual yield
    full_join(annYields) %>% 
    mutate(prop_NO3_yield = tot_NO3_yield/ann_NO3_yield) %>% 
    # Exclude 2017 events
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(year), y = prop_NO3_yield*100, fill = factor(clust_wat_5cl))) +
      # facet_wrap(~var, ncol = 2, scales = "free_y", labeller = labeller(var = labels_var)) +
      geom_bar(position = "stack", stat = "identity") +
      # scale_fill_manual(name = "Cluster",
      #                   values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7"),
      #                   labels = c("Warm, dry soil, big rain", 
      #                              "Very wet soil, rain/melt",
      #                              "Cold, dry soil, mostly melt",
      #                              "Low sun, wet soil, low-int. rain")) +
      scale_fill_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(atop('%'~event~NO[3]^-{}~yield, "during ice-free season"))) +
      xlab("Year") +
      theme1 +
      theme(axis.text.x = element_blank(),
            axis.title.x = element_blank())
  
  # 6 clusters
  # NOTE: Colors are rearranged here to make clusters align with above 2 models; if anything changes, change these
  p_wd_13 <- som_wd %>%
    # Calculate the cummulative sum of yields for each solute, year, and cluster #
    mutate(year = year(event_start)) %>% 
    # pivot_longer(cols = c(NO3_kg_km2, SRP_kg_km2), names_to = "var", values_to = "value") %>% 
    # group_by(year, cluster, var) %>% 
    group_by(year, clust_wat_6cl) %>% 
    summarize(tot_NO3_yield = sum(NO3_kg_km2, na.rm = TRUE)) %>% 
    ungroup() %>% 
    # Calculate proportion of total annual yield
    full_join(annYields) %>% 
    mutate(prop_NO3_yield = tot_NO3_yield/ann_NO3_yield) %>% 
    # Exclude 2017 events
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(year), y = prop_NO3_yield*100, fill = factor(clust_wat_6cl))) +
      # facet_wrap(~var, ncol = 2, scales = "free_y", labeller = labeller(var = labels_var)) +
      geom_bar(position = "stack", stat = "identity") +
      # scale_fill_manual(name = "Cluster",
      #                   values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7"),
      #                   labels = c("Warm, dry soil, big rain", 
      #                              "Very wet soil, rain/melt",
      #                              "Cold, dry soil, mostly melt",
      #                              "Low sun, wet soil, low-int. rain")) +
      scale_fill_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(atop('%'~event~NO[3]^-{}~yield, "during ice-free season"))) +
      xlab("Year") +
      theme1  
  
  # Combine into one plot
  (p_wd_8 + p_wd_11) / (p_wd_9 + p_wd_12) / (p_wd_10 + p_wd_13) +
    plot_annotation(
      title = "Wade"
    )  
```
Total ice-free season water yield attributed to each cluster.
<br><br>

```{r cluster, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE, fig.asp = 0.7}
# Plot boxplots of water yields attributed to each cluster
# HFORD
  # 4 clusters
  pl_hf_x1 <- som_hf %>%
    mutate(year = year(event_start)) %>% 
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(clust_wat_4cl), y = NO3_kg_km2, color = factor(clust_wat_4cl))) +
    facet_wrap(~year) +
    geom_boxplot() +
    scale_color_manual(name = "Cluster",
                      values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
    ylab(expression(atop(Event~NO[3]^-{}~yield, (kg~N~km^{-2})))) +
    xlab("Cluster") +
    theme1 +
    theme(legend.position = "none",
          strip.background = element_blank(),
          strip.text.x = element_text(size = 12),
          axis.title.x = element_blank()) +
  ggtitle("HF - 4 cl. model")

  # 5 clusters
  pl_hf_x2 <- som_hf %>%
    mutate(year = year(event_start)) %>% 
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(clust_wat_5cl), y = NO3_kg_km2, color = factor(clust_wat_5cl))) +
    facet_wrap(~year) +
    geom_boxplot() +
    scale_color_manual(name = "Cluster",
                      values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
    ylab(expression(atop(Event~NO[3]^-{}~yield, (kg~N~km^{-2})))) +
    xlab("Cluster") +
    theme1 +
    theme(legend.position = "none",
          strip.background = element_blank(),
          strip.text.x = element_blank(),
          axis.title.x = element_blank()) +
  ggtitle("HF - 5 cl. model")
  
  # 6 clusters
  pl_hf_x3 <- som_hf %>%
    mutate(year = year(event_start)) %>% 
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(clust_wat_6cl), y = NO3_kg_km2, color = factor(clust_wat_6cl))) +
    facet_wrap(~year) +
    geom_boxplot() +
    scale_color_manual(name = "Cluster",
                      values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
    ylab(expression(atop(Event~NO[3]^-{}~yield, (kg~N~km^{-2})))) +
    xlab("Cluster") +
    theme1 +
    theme(legend.position = "none",
          strip.background = element_blank(),
          strip.text.x = element_blank()) +
  ggtitle("HF - 6 cl. model")
  
# WADE
  # 4 clusters
  pl_wd_x1 <- som_wd %>%
    mutate(year = year(event_start)) %>% 
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(clust_wat_4cl), y = NO3_kg_km2, color = factor(clust_wat_4cl))) +
    facet_wrap(~year) +
    geom_boxplot() +
    scale_color_manual(name = "Cluster",
                      values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
    ylab(expression(atop(Event~NO[3]^-{}~yield, (kg~N~km^{-2})))) +
    xlab("Cluster") +
    theme1 +
    theme(legend.position = "none",
          strip.background = element_blank(),
          strip.text.x = element_text(size = 12),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
  ggtitle("WD - 4 cl. model")

  # 5 clusters
  pl_wd_x2 <- som_wd %>%
    mutate(year = year(event_start)) %>% 
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(clust_wat_5cl), y = NO3_kg_km2, color = factor(clust_wat_5cl))) +
    facet_wrap(~year) +
    geom_boxplot() +
    scale_color_manual(name = "Cluster",
                      values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
    ylab(expression(atop(Event~NO[3]^-{}~yield, (kg~N~km^{-2})))) +
    xlab("Cluster") +
    theme1 +
    theme(legend.position = "none",
          strip.background = element_blank(),
          strip.text.x = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
  ggtitle("WD - 5 cl. model")
  
  # 6 clusters
  pl_wd_x3 <- som_wd %>%
    mutate(year = year(event_start)) %>% 
    filter(year != 2017) %>% 
    ggplot(aes(x = factor(clust_wat_6cl), y = NO3_kg_km2, color = factor(clust_wat_6cl))) +
    facet_wrap(~year) +
    geom_boxplot() +
    scale_color_manual(name = "Cluster",
                      values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
    ylab(expression(atop(Event~NO[3]^-{}~yield, (kg~N~km^{-2})))) +
    xlab("Cluster") +
    theme1 +
    theme(legend.position = "none",
          strip.background = element_blank(),
          strip.text.x = element_blank(),
          axis.title.y = element_blank()) +
  ggtitle("WD - 6 cl. model")
  
# Combine plots
  pl_c_hf1 <- pl_hf_x1 / pl_hf_x2 / pl_hf_x3 +
    plot_annotation(
      title = "Hungerford"
    )
  
  pl_c_wd1 <- pl_wd_x1 / pl_wd_x2 / pl_wd_x3 +
    plot_annotation(
      title = "Wade"
    ) 
  
  pl_c_hf1 | pl_c_wd1
```
Event water yields attributed to each cluster. 2017 data not shown because only a few events in fall. Recall that cluster 1 in the first model is not necessarily the same as cluster 1 in another model.
<br><br>

##### Relationship between event NO3, SRP, or turbidity yield and event water yield for each season
```{r regressions, include=FALSE, warning=FALSE, message = FALSE}
# Which events and yields have an SOM cluster assigned (excluding SOM water yield)
yesCluster <- 
  som_results %>% 
  filter(SOM != "water") %>% 
  select(site, SOM, season, event_start, clust_4cl, clust_5cl, clust_6cl) %>% 
  # pivot_wider(names_from = SOM, values_from = clust_4cl) %>%
  mutate(clust_YN = ifelse(!is.na(clust_4cl), "yes", "no")) %>% 
  rename(var = SOM)

# Join to a df with event info and yield estimates to filter out events with not assigned cluster for each var (NO3, SRP, turb)
datWithClusters <-
  bind_rows(hford, wade) %>% 
  select(site, season, event_start, ends_with("km2"), q_mm) %>% 
  pivot_longer(cols = c(NO3_kg_km2, SRP_kg_km2, turb_kg_km2), names_to = "var", values_to = "yield") %>% 
  left_join(yesCluster, by = c("site", "season", "event_start", "var")) %>% 
  filter(clust_YN == "yes") %>% 
  select(-clust_YN)
  
# Regress event yield on event water yield
# Get stats on coefficient estimates
lm_results_coef <- 
  datWithClusters %>% 
  # Group and nest these groupings
  group_by(site, season, var) %>% 
  nest() %>% 
  mutate(model = map(data, ~ lm(yield ~ q_mm, data = .x)),
         tidied = map(model, tidy)) %>% 
  unnest(tidied) %>% 
  filter(term != "(Intercept)") %>% 
  select(-c(data, model)) %>% 
  ungroup()

# Get R^2 and other summary stats
lm_results_r2 <-
  datWithClusters %>% 
  # Group and nest these groupings
  group_by(site, season, var) %>% 
  nest() %>% 
  mutate(model = map(data, ~ lm(yield ~ q_mm, data = .x)),
         glanced = map(model, glance),
         augmented = map(model, augment)) %>% 
  unnest(glanced) %>% 
  select(-c(data, model)) %>% 
  ungroup()

# Join these together
lm_results <- 
  full_join(lm_results_coef, lm_results_r2, by = c("var", "site", "season")) %>% 
  unnest(augmented)
rm(lm_results_coef, lm_results_r2)

# Add event & SOM cluster assign info to this df
allData <- 
  lm_results %>% 
  left_join(datWithClusters, by = c("site", "season", "var", "yield", "q_mm")) %>% 
  left_join(som_results %>% 
              rename(var = SOM) %>% 
              select(-c(NO3_kg_km2, SRP_kg_km2, turb_kg_km2))) %>% 
  select(site, event_start, starts_with("clust"), everything()) %>% 
  arrange(site, event_start)

# allData %>% 
#   mutate(event_start = as.character(event_start)) %>% 
#   write_csv("Data/results_clusters_withLinearRegressions.csv")

```

```{r, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
# Plot NO3, SRP, & turbidity yields against water yield
# HFORD - NOTE: might need to do segmented regression for turbidity fit
  # Faceted by solute
  pl_1 <- 
    allData %>% 
    filter(site == "Hungerford") %>% 
    mutate(season = factor(season, levels = c("spring", "summer", "fall"), labels = c("Spring", "Summer", "Fall"))) %>% 
    # Adding the expressions as labels requires that you add labeller = label_parsed in the facet_* call below
    mutate(var = factor(var, levels = c("NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), labels = c(expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>% 
    ggplot(aes(x = q_mm, y = yield)) +
      facet_grid(var~season, scales = "free", labeller = label_parsed) +
      geom_smooth(method=lm, se=FALSE, color = "black") +
      geom_point(aes(color = factor(clust_5cl), shape = factor(year(event_start))), size = 2, stroke = 0.75, alpha = 0.8) +
      scale_shape_manual(name = "Season",
                         values = c(19, 17, 15)) +
      scale_color_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(Event~NO[3]^-{}~or~SRP~or~turb.~yield)) +
      xlab("Event water yield (mm)") +
      theme1 +
      theme(strip.background = element_blank(),
            legend.position = "none") +
      ggtitle("Hungerford")

  # Faceted by solute and season
  pl_2 <- 
    allData %>% 
    filter(site == "Hungerford") %>% 
    mutate(season = factor(season, levels = c("spring", "summer", "fall"), labels = c("Spring", "Summer", "Fall"))) %>% 
    # Adding the expressions as labels requires that you add labeller = label_parsed in the facet_* call below
    mutate(var = factor(var, levels = c("NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), labels = c(expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>% 
    ggplot(aes(x = q_mm, y = yield)) +
      facet_grid(var~season, scales = "free", labeller = label_parsed) +
      geom_smooth(method=lm, se=FALSE, color = "black") +
      geom_point(aes(color = factor(clust_5cl), shape = factor(year(event_start))), size = 2, stroke = 0.75, alpha = 0.8) +
      scale_shape_manual(name = "Year",
                         values = c(19, 17, 15)) +
      scale_color_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(Event~NO[3]^-{}~or~SRP~or~turb.~yield)) +
      xlab("Event water yield (mm)") +
      theme1 +
      theme(strip.background = element_blank(),
            axis.title.x = element_blank(),
            legend.position = "none") +
      ggtitle("Hungerford")
  
    # Plot standardized residuals
    pl_3 <-
      allData %>% 
      filter(site == "Hungerford") %>% 
      mutate(season = factor(season, levels = c("spring", "summer", "fall"), labels = c("Spring", "Summer", "Fall"))) %>% 
      mutate(var = factor(var, levels = c("NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), labels = c(expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>%   
      ggplot(aes(x = q_mm, y = .std.resid)) +
      facet_grid(var~season, scales = "free", labeller = label_parsed) +
      geom_hline(yintercept = 0, color = "black", linetype = "dashed") +
      geom_hline(yintercept = -2, color = "gray80", linetype = "dashed") +
      geom_hline(yintercept = 2, color = "gray80", linetype = "dashed") +
      geom_point(aes(color = factor(clust_5cl), shape = factor(year(event_start))), size = 2, stroke = 0.75, alpha = 0.8) +
      scale_shape_manual(name = "Year",
                   values = c(19, 17, 15)) +
      scale_color_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +  
      ylab("Std. residuals") +
      xlab("Event water yield (mm)") +
      theme1 +
      theme(strip.background = element_blank(),
            axis.title.x = element_blank(),
            strip.text.x = element_blank())

# WADE - NOTE: might need to do segmented regression for turbidity fit
  # Faceted by solute
  pl_4 <- 
    allData %>% 
    filter(site == "Wade") %>% 
    filter(season != "winter") %>% 
    mutate(season = factor(season, levels = c("spring", "summer", "fall"), labels = c("Spring", "Summer", "Fall"))) %>% 
    # Adding the expressions as labels requires that you add labeller = label_parsed in the facet_* call below
    mutate(var = factor(var, levels = c("NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), labels = c(expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>% 
    ggplot(aes(x = q_mm, y = yield)) +
      facet_grid(var~season, scales = "free", labeller = label_parsed) +
      geom_smooth(method=lm, se=FALSE, color = "black") +
      geom_point(aes(color = factor(clust_5cl), shape = factor(year(event_start))), size = 2, stroke = 0.75, alpha = 0.8) +
      scale_shape_manual(name = "Season",
                         values = c(19, 17, 15)) +
      scale_color_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(Event~NO[3]^-{}~or~SRP~or~turb.~yield)) +
      xlab("Event water yield (mm)") +
      theme1 +
      theme(strip.background = element_blank(),
            axis.title.y = element_blank()) +
      ggtitle("Wade")
  
  # Faceted by solute and season  
  pl_5 <-
    allData %>% 
    filter(site == "Wade") %>% 
    filter(season != "winter") %>% 
    mutate(season = factor(season, levels = c("spring", "summer", "fall"), labels = c("Spring", "Summer", "Fall"))) %>% 
    # Adding the expressions as labels requires that you add labeller = label_parsed in the facet_* call below
    mutate(var = factor(var, levels = c("NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), labels = c(expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>% 
    ggplot(aes(x = q_mm, y = yield)) +
      facet_grid(var~season, scales = "free", labeller = label_parsed) +
      geom_smooth(method=lm, se=FALSE, color = "black") +
      geom_point(aes(color = factor(clust_5cl), shape = factor(year(event_start))), size = 2, stroke = 0.75, alpha = 0.8) +
      scale_shape_manual(name = "Year",
                   values = c(19, 17, 15)) +
      scale_color_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(Event~NO[3]^-{}~or~SRP~or~turb.~yield)) +
      xlab("Event water yield (mm)") +
      theme1 +
      theme(strip.background = element_blank(),
            strip.text.x = element_blank(),
            legend.position = "none") +
      ggtitle("Wade") 
  
  # Plot standardized residuals
  pl_6 <- 
    allData %>% 
    filter(season != "winter") %>% 
    filter(site == "Wade") %>% 
    mutate(season = factor(season, levels = c("spring", "summer", "fall"), labels = c("Spring", "Summer", "Fall"))) %>% 
    mutate(var = factor(var, levels = c("NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), labels = c(expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>%   
    ggplot(aes(x = q_mm, y = .std.resid)) +
    facet_grid(var~season, scales = "free", labeller = label_parsed) +
    geom_hline(yintercept = 0, color = "black", linetype = "dashed") +
    geom_hline(yintercept = -2, color = "gray80", linetype = "dashed") +
    geom_hline(yintercept = 2, color = "gray80", linetype = "dashed") +
    geom_point(aes(color = factor(clust_5cl), shape = factor(year(event_start))), size = 2, stroke = 0.75, alpha = 0.8) +
    scale_shape_manual(name = "Year",
                 values = c(19, 17, 15)) +    
    scale_color_manual(name = "Cluster",
                      values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +    
    ylab("Std. residuals") +
    xlab("Event water yield (mm)") +
    theme1 +
    theme(strip.background = element_blank(),
          strip.text.x = element_blank())  

# Combine plots
  # Seasonal plots
  (pl_2 | pl_3) / (pl_5 | pl_6)
```
May need to look at segmented regression, especially for turbidity
<br><br>

##### Event NO3 to SRP yield ratios

