---
title: <font size = "5"> Summary figures for all SOM event yield results </font>
author: "Dustin Kincaid"
date: "04/26/2021<br><br>"
output: html_document
editor_options: 
  chunk_output_type: console
---

### Objective  
##### Create key figures for paper summarizing all results of SOM clustered flux regimes on event water, NO3, SRP, and turbidity yields from Hungerford and Wade Brooks. Note: these current figures assume that the best SOM model for every site X variable combo has 5 clusters. This seems to often be the case, but I have not yet evaluated every site X variable combo. Also note that these figures are not in their final format.

### Feedback request  
##### I'm mainly looking for ways to frame this story about the influence of watershed conditions and event characteristics on yields from the two catchments with different primary land uses. I am also looking for suggestions for different analyses and/or ways to visualize the data. All other general feedback is welcome as well.
<br><br>

```{r setup, include=FALSE, warning=FALSE, message = FALSE}
# Set defaults
knitr::opts_chunk$set(fig.width = 6, fig.asp = 0.618, out.width = "70%", fig.align = "center")

# Load packages
  library("here")      # to make file paths fail less
  library("tidyverse") # general workhorse
  library("lubridate") # to work with dates
  library("patchwork") # arranging multiple plots
  library("broom")     # for linear regressions
```

```{r data, include=FALSE, warning=FALSE, message = FALSE}
# Read in data
  # Calculated event metrics for each site as calculated in compile_calculate_allVars.R
  hford <- read_csv(here("Data", "eventMetrics_hford.csv")) %>% 
    mutate(event_start = ymd_hms(event_start, tz = "Etc/GMT+4"))

  wade <- read_csv(here("Data", "eventMetrics_wade.csv")) %>% 
    mutate(event_start = ymd_hms(event_start, tz = "Etc/GMT+4"))

  # SOM results from SOManalysis_SITE_yields_VAR.Rmd
  # Water
  som_wat_hf <- read_csv(here("Data", "somResults", "hford", "yields", "water", "2021-04-07", "Results_hford_withClusters.csv")) %>% mutate(SOM = "water") %>% select(site, SOM, everything())
  som_wat_wd <- read_csv(here("Data", "somResults", "wade", "yields", "water", "2021-04-07", "Results_wade_withClusters.csv")) %>% mutate(SOM = "water") %>% select(site, SOM, everything())
  # NO3
  som_no3_hf <- read_csv(here("Data", "somResults", "hford", "yields", "NO3", "2021-04-08", "Results_hford_withClusters.csv")) %>% mutate(SOM = "NO3_kg_km2") %>% select(site, SOM, everything())
  som_no3_wd <- read_csv(here("Data", "somResults", "wade", "yields", "NO3", "2021-04-12", "Results_wade_withClusters.csv")) %>% mutate(SOM = "NO3_kg_km2") %>% select(site, SOM, everything())
  # SRP
  som_srp_hf <- read_csv(here("Data", "somResults", "hford", "yields", "SRP", "2021-04-08", "Results_hford_withClusters.csv")) %>% mutate(SOM = "SRP_kg_km2") %>% select(site, SOM, everything())
  som_srp_wd <- read_csv(here("Data", "somResults", "wade", "yields", "SRP", "2021-04-12", "Results_wade_withClusters.csv")) %>% mutate(SOM = "SRP_kg_km2") %>% select(site, SOM, everything())
  # Turbidity
  som_turb_hf <- read_csv(here("Data", "somResults", "hford", "yields", "turb", "2021-04-09", "Results_hford_withClusters.csv")) %>% mutate(SOM = "turb_kg_km2") %>% select(site, SOM, everything())
  som_turb_wd <- read_csv(here("Data", "somResults", "wade", "yields", "turb", "2021-04-13", "Results_wade_withClusters.csv")) %>% mutate(SOM = "turb_kg_km2") %>% select(site, SOM, everything())
  
# Join SOM results into one df per site
  som_results <- bind_rows(som_wat_hf, som_wat_wd, som_no3_hf, som_no3_wd, som_srp_hf, som_srp_wd, som_turb_hf, som_turb_wd) %>% 
    rename(clust_4cl = clust_wat_4cl, clust_5cl = clust_wat_5cl, clust_6cl = clust_wat_6cl) %>% 
    mutate(event_start = ymd_hms(event_start, tz = "Etc/GMT+4"))
  rm(som_wat_hf, som_wat_wd, som_no3_hf, som_no3_wd, som_srp_hf, som_srp_wd, som_turb_hf, som_turb_wd)
```

```{r plot themes and labels, include = FALSE}
# Plotting specifics
  theme1 <- theme_classic() +
            theme(axis.text = element_text(size = 11),
                  axis.title = element_text(size = 12),
                  axis.title.x = element_text(margin=margin(5,0,0,0)),
                  axis.title.y = element_text(margin=margin(0,5,0,0)),
                  legend.title = element_text(size = 9),
                  legend.text = element_text(size = 9),
                  strip.text = element_text(size = 12))
  
  # A new theme for the hysteresis plots
  theme2 <- theme(axis.line = element_blank(),
                  axis.text = element_text(size = 8),
                  axis.title = element_blank(),
                  plot.margin = unit(c(1.25,1.25,1.25,1.25), "lines"),
                  panel.background = element_blank(),
                  panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank(),
                  legend.text = element_text(size = 6),
                  legend.key.size = unit(0.1, "in"),
                  legend.margin = margin(0, 0, 0, 0),
                  legend.title = element_text(size = 6)) 
```

```{r timeline, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 11, fig.asp = .7, out.width = "100%"}
# Plot timeline of event water yields & ratios colored by cluster number
# NOTE: THESE PLOTS ASSUME THAT A 5 CLUSTER SOM MODEL IS APPROPRIATE FOR ALL SITE x VAR COMBO; ALTER IF NOT APPROPRIATE
# HFORD
  # Create a dataframe that drops event dates that only have Q yield
  hf_yields <- 
    som_results %>% 
    filter(site == "Hungerford") %>% 
    pivot_longer(cols = c(q_mm, NO3_kg_km2, SRP_kg_km2, turb_kg_km2), names_to = "var", values_to = "yield") %>% 
    mutate(year = year(event_start)) %>% 
    select(site, event_start, year, SOM, clust_5cl, gw_1d_well5, var, yield) %>% 
    filter((SOM == "water" & var == "q_mm") |
             (SOM == "NO3_kg_km2" & var == "NO3_kg_km2") |
             (SOM == "SRP_kg_km2" & var == "SRP_kg_km2") |
             (SOM == "turb_kg_km2" & var == "turb_kg_km2")) %>% 
    mutate(var = factor(var, 
                    levels = c("q_mm", "NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), 
                    labels = c(expression(Q~(mm)), expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>%   
    # Only 2 events in 2017, so cutting out 2017
    filter(year(event_start) != 2017) %>%
     # Add leading zero to single digit months and days
    mutate(year = year(event_start),
           month = str_pad(month(event_start), 2, pad = 0),
           day = str_pad(day(event_start), 2, pad = 0),
           month_day = paste(month, "/", day, sep = "")) %>%
    # There is one day where there are two events, add a rep for month_day and make month_day_rep ID
    group_by(SOM, year, month_day) %>% 
    mutate(rep = row_number()) %>% 
    mutate(month_day_rep = paste(month_day, rep, sep = "-")) %>% 
    filter(!(event_start >= ymd_hms("2019-01-01 00:00:00", tz = "Etc/GMT+4") & event_start <= ymd_hms("2019-03-29 00:00:00", tz = "Etc/GMT+4")))


  # First graph GW level data along with water yield timeline
  # Text for missing data on 2019 plot
  ann_text <- data.frame(month_day_rep = "03/26-2", gw_1d_well5 = -0.35, lab = "No \n data",
                         year = factor(2019, levels = c("2018", "2019")))
  # GW Plot
  pl_hf_gw <- 
    hf_yields %>% 
    filter(SOM == "water") %>% 
    ggplot(aes(x = month_day_rep, y = gw_1d_well5)) +
      facet_wrap(~year, scales = "free_x", ncol = 2) +
      geom_bar(stat = "identity", fill = "white") +
      ylab("GW level \n (m below \n soil surface)") +
      xlab("Date (month/day - #)") +
      scale_y_continuous(expand = c(0, 0)) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.background = element_rect(fill = "lightblue"),
            strip.text.x = element_text(size = 8),
            axis.text.x = element_blank(),
            axis.title.x = element_blank()) +
    geom_text(data = ann_text, label = "No \n data")

  # 5 cluster model
  pl_hf_1 <- 
    hf_yields %>% 
    ggplot(aes(x = factor(month_day_rep), y = yield, fill = as.factor(clust_5cl))) +
      facet_grid(var~year, scale = "free", labeller = label_parsed) +
      geom_bar(stat = "identity") +
      scale_fill_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab("Event yield") +
      xlab("Date (month/day - #)") +
      theme1 +
      theme(axis.text.x = element_text(angle = 90),
            strip.background = element_blank(),
            strip.text.y = element_text(size = 9))
  
# WADE
  # Create a dataframe that drops event dates that only have Q yield
  wd_yields <- 
    som_results %>% 
    filter(site == "Wade") %>% 
    pivot_longer(cols = c(q_mm, NO3_kg_km2, SRP_kg_km2, turb_kg_km2), names_to = "var", values_to = "yield") %>% 
    mutate(year = year(event_start)) %>% 
    select(site, event_start, year, SOM, clust_5cl, gw_1d_well5, var, yield) %>% 
    filter((SOM == "water" & var == "q_mm") |
             (SOM == "NO3_kg_km2" & var == "NO3_kg_km2") |
             (SOM == "SRP_kg_km2" & var == "SRP_kg_km2") |
             (SOM == "turb_kg_km2" & var == "turb_kg_km2")) %>% 
    mutate(var = factor(var, 
                    levels = c("q_mm", "NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), 
                    labels = c(expression(Q~(mm)), expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>%   
    # Only 2 events in 2017, so cutting out 2017
    filter(year(event_start) != 2017) %>%
     # Add leading zero to single digit months and days
    mutate(year = year(event_start),
           month = str_pad(month(event_start), 2, pad = 0),
           day = str_pad(day(event_start), 2, pad = 0),
           month_day = paste(month, "/", day, sep = "")) %>%
    # There is one day where there are two events, add a rep for month_day and make month_day_rep ID
    group_by(SOM, year, month_day) %>% 
    mutate(rep = row_number()) %>% 
    mutate(month_day_rep = paste(month_day, rep, sep = "-"))
    # filter(!(event_start >= ymd_hms("2019-01-01 00:00:00", tz = "Etc/GMT+4") & event_start <= ymd_hms("2019-03-29 00:00:00", tz = "Etc/GMT+4")))

  # GW Plot
  pl_wd_gw <- 
    wd_yields %>% 
    filter(SOM == "water") %>% 
    ggplot(aes(x = month_day_rep, y = gw_1d_well5)) +
      facet_wrap(~year, scales = "free_x", ncol = 2) +
      geom_bar(stat = "identity", fill = "white") +
      ylab("GW level \n (m below \n soil surface)") +
      xlab("Date (month/day - #)") +
      scale_y_continuous(expand = c(0, 0)) +
      theme_bw() +
      theme(panel.grid = element_blank(),
            panel.background = element_rect(fill = "lightblue"),
            strip.text.x = element_text(size = 8),
            axis.text.x = element_blank(),
            axis.title.x = element_blank())

  # 5 cluster model
  pl_wd_1 <- 
    wd_yields %>% 
    ggplot(aes(x = factor(month_day_rep), y = yield, fill = as.factor(clust_5cl))) +
      facet_grid(var~year, scale = "free", labeller = label_parsed) +
      geom_bar(stat = "identity") +
      scale_fill_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab("Event yield") +
      xlab("Date (month/day - #)") +
      theme1 +
      theme(axis.text.x = element_text(angle = 90),
            strip.background = element_blank(),
            strip.text.y = element_text(size = 9))
  
# Combine the plots into one using the patchwork library
  # HFORD
  pl_hf_gw / pl_hf_1 +
    plot_layout(
      ncol = 1, 
      heights = c(0.75, 4)) +
    plot_annotation(
      title = "Hungerford"
    )
  rm(pl_hf_gw, pl_hf_1) 
  
  # WADE
  pl_wd_gw / pl_wd_1 +
    plot_layout(
      ncol = 1, 
      heights = c(0.75, 4)) +
    plot_annotation(
      title = "Wade"
    )
  rm(pl_wd_gw, pl_wd_1)    
```  
Time series of water yields colored by cluster. 2017 data not shown because only a few events in fall. The white bars in the upper groundwater level plot indicate the groundwater depth below the soil surface. Keep in mind that a different SOM was created for each site x variable (e.g., NO3, SRP) combo; thus, the clusters may not have the same properties for each site x variable combination.
<br><br>

##### Ice-free season yields attributed to each cluster
```{r contr of clust to yields, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 10, fig.asp = 1, out.width = "100%"}
# Plot total yield attributed to each cluster
  # Calculate annual measured event yields
  annYields <-
    som_results %>%
    pivot_longer(cols = c(q_mm, NO3_kg_km2, SRP_kg_km2, turb_kg_km2), names_to = "var", values_to = "yield") %>% 
    mutate(year = year(event_start)) %>% 
    select(site, year, SOM, var, yield) %>% 
    filter((SOM == "water" & var == "q_mm") |
             (SOM == "NO3_kg_km2" & var == "NO3_kg_km2") |
             (SOM == "SRP_kg_km2" & var == "SRP_kg_km2") |
             (SOM == "turb_kg_km2" & var == "turb_kg_km2")) %>% 
    group_by(site, year, SOM, var) %>% 
    summarize(ann_tot_yield = sum(yield, na.rm = TRUE)) %>% 
    ungroup()

  # Calculate amount of annual yields per cluster
  # NOTE: IF CHOOSING A DIFFERENT CLUSTER MODEL, NEED TO CHANGE THIS CODE
  # RIGHT NOW THIS CODE JUST ASSUMES ONE CLUSTER MODEL (5 clusters) FOR EACH SITE AND SOM
  # Might be able to just choose one cluster model when reading in the som results above and then name the column the same
  annYields_perCluster <-
    som_results %>% 
    pivot_longer(cols = c(q_mm, NO3_kg_km2, SRP_kg_km2, turb_kg_km2), names_to = "var", values_to = "yield") %>% 
    mutate(year = year(event_start)) %>% 
    select(site, year, SOM, clust_5cl, var, yield) %>% 
    filter((SOM == "water" & var == "q_mm") |
             (SOM == "NO3_kg_km2" & var == "NO3_kg_km2") |
             (SOM == "SRP_kg_km2" & var == "SRP_kg_km2") |
             (SOM == "turb_kg_km2" & var == "turb_kg_km2")) %>% 
    group_by(site, SOM, var, year, clust_5cl) %>% 
    summarize(ann_clust_yield = sum(yield, na.rm = TRUE)) %>% 
    ungroup()
  
  # Join these together
  # And calculate proportion of total annual yield attributed to each cluster
  annYields_summ <-
    full_join(annYields_perCluster, annYields, by = c("site", "SOM", "var", "year")) %>% 
    mutate(prop_clust_yield = ann_clust_yield/ann_tot_yield)
  rm(annYields, annYields_perCluster)
    

  # Stacked bar graph (year on x-axis; stacks = yields by cluster)
  # Total & proportional annual event yield per cluster
    # HFORD - 5 clusters
    pl_hf_2 <- 
      annYields_summ %>%
      filter(site == "Hungerford") %>% 
      pivot_longer(cols = c(ann_clust_yield, prop_clust_yield), names_to = "yield_cat", values_to = "yield") %>% 
      mutate(yield_cat = factor(yield_cat, 
                          levels = c("ann_clust_yield", "prop_clust_yield"),
                          labels = c(expression(Total~yield), expression(Prop.~yield)))) %>% 
      mutate(var = factor(var, 
                          levels = c("q_mm", "NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), 
                          labels = c(expression(Q~(mm)), expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>% 
      # Exclude 2017 events  
      filter(year != 2017) %>% 
      ggplot(aes(x = factor(year), y = yield, fill = factor(clust_5cl))) + 
        facet_wrap(var~yield_cat, ncol = 2, scales = "free_y", labeller = label_parsed) +
        geom_bar(position = "stack", stat = "identity") +
        scale_fill_manual(name = "Cluster",
                          values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
        ylab(expression(atop(Event~total~or~prop.~yield, "during ice-free season"))) +
        xlab("Year") +
        theme1 +
        theme(axis.title.x = element_blank(),
              strip.background = element_blank()) +
      ggtitle("Hungerford")
    
    # WADE - 5 clusters
    pl_wd_2 <- 
      annYields_summ %>%
      filter(site == "Wade") %>% 
      pivot_longer(cols = c(ann_clust_yield, prop_clust_yield), names_to = "yield_cat", values_to = "yield") %>% 
      mutate(yield_cat = factor(yield_cat, 
                          levels = c("ann_clust_yield", "prop_clust_yield"),
                          labels = c(expression(Total~yield), expression(Prop.~yield)))) %>% 
      mutate(var = factor(var, 
                          levels = c("q_mm", "NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), 
                          labels = c(expression(Q~(mm)), expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>% 
      # Exclude 2017 events  
      filter(year != 2017) %>% 
      ggplot(aes(x = factor(year), y = yield, fill = factor(clust_5cl))) + 
        facet_wrap(var~yield_cat, ncol = 2, scales = "free_y", labeller = label_parsed) +
        geom_bar(position = "stack", stat = "identity") +
        scale_fill_manual(name = "Cluster",
                          values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
        ylab(expression(atop(Event~total~or~prop.~yield, "during ice-free season"))) +
        xlab("Year") +
        theme1 +
        theme(axis.title.x = element_blank(),
              strip.background = element_blank()) +
      ggtitle("Wade")     

  
  # Print
  pl_hf_2
  pl_wd_2
  
```
Total ice-free season water yield attributed to each cluster. Keep in mind that a different SOM was created for each site x variable (e.g., NO3, SRP) combo; thus, the clusters may not have the same properties for each site x variable combination.
<br><br>

##### Relationship between event NO3, SRP, or turbidity yield and event water yield for each season
```{r regressions, include=FALSE, warning=FALSE, message = FALSE}
# Which events and yields have an SOM cluster assigned (excluding SOM water yield)
yesCluster <- 
  som_results %>% 
  filter(SOM != "water") %>% 
  select(site, SOM, season, event_start, clust_4cl, clust_5cl, clust_6cl) %>% 
  # pivot_wider(names_from = SOM, values_from = clust_4cl) %>%
  mutate(clust_YN = ifelse(!is.na(clust_4cl), "yes", "no")) %>% 
  rename(var = SOM)

# Join to a df with event info and yield estimates to filter out events with not assigned cluster for each var (NO3, SRP, turb)
datWithClusters <-
  bind_rows(hford, wade) %>% 
  select(site, season, event_start, ends_with("km2"), q_mm) %>% 
  pivot_longer(cols = c(NO3_kg_km2, SRP_kg_km2, turb_kg_km2), names_to = "var", values_to = "yield") %>% 
  left_join(yesCluster, by = c("site", "season", "event_start", "var")) %>% 
  filter(clust_YN == "yes") %>% 
  select(-clust_YN)
  
# Regress event yield on event water yield
# Get stats on coefficient estimates
lm_results_coef <- 
  datWithClusters %>% 
  # Group and nest these groupings
  group_by(site, season, var) %>% 
  nest() %>% 
  mutate(model = map(data, ~ lm(yield ~ q_mm, data = .x)),
         tidied = map(model, tidy)) %>% 
  unnest(tidied) %>% 
  filter(term != "(Intercept)") %>% 
  select(-c(data, model)) %>% 
  ungroup()

# Get R^2 and other summary stats
lm_results_r2 <-
  datWithClusters %>% 
  # Group and nest these groupings
  group_by(site, season, var) %>% 
  nest() %>% 
  mutate(model = map(data, ~ lm(yield ~ q_mm, data = .x)),
         glanced = map(model, glance),
         augmented = map(model, augment)) %>% 
  unnest(glanced) %>% 
  select(-c(data, model)) %>% 
  ungroup()

# Join these together
lm_results <- 
  full_join(lm_results_coef, lm_results_r2, by = c("var", "site", "season")) %>% 
  unnest(augmented)
rm(lm_results_coef, lm_results_r2)

# Add event & SOM cluster assign info to this df
allData <- 
  lm_results %>% 
  left_join(datWithClusters, by = c("site", "season", "var", "yield", "q_mm")) %>% 
  left_join(som_results %>% 
              rename(var = SOM) %>% 
              select(-c(NO3_kg_km2, SRP_kg_km2, turb_kg_km2))) %>% 
  select(site, event_start, starts_with("clust"), everything()) %>% 
  arrange(site, event_start)

# allData %>% 
#   mutate(event_start = as.character(event_start)) %>% 
#   write_csv("Data/results_clusters_withLinearRegressions.csv")

```

```{r, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 9, fig.asp = 0.6, out.width = "100%"}
#fig.width = 10, fig.asp = .7, out.width = "100%"

# Plot NO3, SRP, & turbidity yields against water yield
# NOTE: THESE PLOTS ASSUME THAT A 5 CLUSTER SOM MODEL IS APPROPRIATE FOR ALL SITE x VAR COMBO; ALTER IF NOT APPROPRIATE
# HFORD - NOTE: might need to do segmented regression for turbidity fit
  # Faceted by solute
  pl_1 <- 
    allData %>% 
    filter(site == "Hungerford") %>% 
    mutate(season = factor(season, levels = c("spring", "summer", "fall"), labels = c("Spring", "Summer", "Fall"))) %>% 
    # Adding the expressions as labels requires that you add labeller = label_parsed in the facet_* call below
    mutate(var = factor(var, levels = c("NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), labels = c(expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>% 
    ggplot(aes(x = q_mm, y = yield)) +
      facet_grid(var~season, scales = "free", labeller = label_parsed) +
      geom_smooth(method=lm, se=FALSE, color = "black") +
      geom_point(aes(color = factor(clust_5cl), shape = factor(year(event_start))), size = 2, stroke = 0.75, alpha = 0.8) +
      scale_shape_manual(name = "Season",
                         values = c(19, 17, 15)) +
      scale_color_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(Event~NO[3]^-{}~or~SRP~or~turb.~yield)) +
      xlab("Event water yield (mm)") +
      theme1 +
      theme(strip.background = element_blank(),
            legend.position = "none") +
      ggtitle("Hungerford")

  # Faceted by solute and season
  pl_2 <- 
    allData %>% 
    filter(site == "Hungerford") %>% 
    mutate(season = factor(season, levels = c("spring", "summer", "fall"), labels = c("Spring", "Summer", "Fall"))) %>% 
    # Adding the expressions as labels requires that you add labeller = label_parsed in the facet_* call below
    mutate(var = factor(var, levels = c("NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), labels = c(expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>% 
    ggplot(aes(x = q_mm, y = yield)) +
      facet_grid(var~season, scales = "free", labeller = label_parsed) +
      geom_smooth(method=lm, se=FALSE, color = "black") +
      geom_point(aes(color = factor(clust_5cl), shape = factor(year(event_start))), size = 2, stroke = 0.75, alpha = 0.8) +
      scale_shape_manual(name = "Year",
                         values = c(19, 17, 15)) +
      scale_color_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(Event~NO[3]^-{}~or~SRP~or~turb.~yield)) +
      xlab("Event water yield (mm)") +
      theme1 +
      theme(strip.background = element_blank(),
            legend.position = "none") +
      ggtitle("Hungerford")
  
    # Plot standardized residuals
    pl_3 <-
      allData %>% 
      filter(site == "Hungerford") %>% 
      mutate(season = factor(season, levels = c("spring", "summer", "fall"), labels = c("Spring", "Summer", "Fall"))) %>% 
      mutate(var = factor(var, levels = c("NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), labels = c(expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>%   
      ggplot(aes(x = q_mm, y = .std.resid)) +
      facet_grid(var~season, scales = "free", labeller = label_parsed) +
      geom_hline(yintercept = 0, color = "black", linetype = "dashed") +
      geom_hline(yintercept = -2, color = "gray80", linetype = "dashed") +
      geom_hline(yintercept = 2, color = "gray80", linetype = "dashed") +
      geom_point(aes(color = factor(clust_5cl), shape = factor(year(event_start))), size = 2, stroke = 0.75, alpha = 0.8) +
      scale_shape_manual(name = "Year",
                   values = c(19, 17, 15)) +
      scale_color_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +  
      ylab("Std. residuals") +
      xlab("Event water yield (mm)") +
      theme1 +
      theme(strip.background = element_blank())

# WADE - NOTE: might need to do segmented regression for turbidity fit
  # Faceted by solute
  pl_4 <- 
    allData %>% 
    filter(site == "Wade") %>% 
    filter(season != "winter") %>% 
    mutate(season = factor(season, levels = c("spring", "summer", "fall"), labels = c("Spring", "Summer", "Fall"))) %>% 
    # Adding the expressions as labels requires that you add labeller = label_parsed in the facet_* call below
    mutate(var = factor(var, levels = c("NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), labels = c(expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>% 
    ggplot(aes(x = q_mm, y = yield)) +
      facet_grid(var~season, scales = "free", labeller = label_parsed) +
      geom_smooth(method=lm, se=FALSE, color = "black") +
      geom_point(aes(color = factor(clust_5cl), shape = factor(year(event_start))), size = 2, stroke = 0.75, alpha = 0.8) +
      scale_shape_manual(name = "Season",
                         values = c(19, 17, 15)) +
      scale_color_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(Event~NO[3]^-{}~or~SRP~or~turb.~yield)) +
      xlab("Event water yield (mm)") +
      theme1 +
      theme(strip.background = element_blank(),
            axis.title.y = element_blank()) +
      ggtitle("Wade")
  
  # Faceted by solute and season  
  pl_5 <-
    allData %>% 
    filter(site == "Wade") %>% 
    filter(season != "winter") %>% 
    mutate(season = factor(season, levels = c("spring", "summer", "fall"), labels = c("Spring", "Summer", "Fall"))) %>% 
    # Adding the expressions as labels requires that you add labeller = label_parsed in the facet_* call below
    mutate(var = factor(var, levels = c("NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), labels = c(expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>% 
    ggplot(aes(x = q_mm, y = yield)) +
      facet_grid(var~season, scales = "free", labeller = label_parsed) +
      geom_smooth(method=lm, se=FALSE, color = "black") +
      geom_point(aes(color = factor(clust_5cl), shape = factor(year(event_start))), size = 2, stroke = 0.75, alpha = 0.8) +
      scale_shape_manual(name = "Year",
                   values = c(19, 17, 15)) +
      scale_color_manual(name = "Cluster",
                        values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +
      ylab(expression(Event~NO[3]^-{}~or~SRP~or~turb.~yield)) +
      xlab("Event water yield (mm)") +
      theme1 +
      theme(strip.background = element_blank(),
            legend.position = "none") +
      ggtitle("Wade") 
  
  # Plot standardized residuals
  pl_6 <- 
    allData %>% 
    filter(season != "winter") %>% 
    filter(site == "Wade") %>% 
    mutate(season = factor(season, levels = c("spring", "summer", "fall"), labels = c("Spring", "Summer", "Fall"))) %>% 
    mutate(var = factor(var, levels = c("NO3_kg_km2", "SRP_kg_km2", "turb_kg_km2"), labels = c(expression(NO[3]^-{}~(kg~N~km^{-2})) , expression(SRP~(kg~P~km^{-2})), expression(Turb.~(Sigma~NTU~km^{-2}))))) %>%   
    ggplot(aes(x = q_mm, y = .std.resid)) +
    facet_grid(var~season, scales = "free", labeller = label_parsed) +
    geom_hline(yintercept = 0, color = "black", linetype = "dashed") +
    geom_hline(yintercept = -2, color = "gray80", linetype = "dashed") +
    geom_hline(yintercept = 2, color = "gray80", linetype = "dashed") +
    geom_point(aes(color = factor(clust_5cl), shape = factor(year(event_start))), size = 2, stroke = 0.75, alpha = 0.8) +
    scale_shape_manual(name = "Year",
                 values = c(19, 17, 15)) +    
    scale_color_manual(name = "Cluster",
                      values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +    
    ylab("Std. residuals") +
    xlab("Event water yield (mm)") +
    theme1 +
    theme(strip.background = element_blank())  

# Combine plots
  # Seasonal plots
  pl_2 | pl_3
  pl_5 | pl_6
```
Need to remove outliers from regressions.
<br><br>

##### Event NO3 to SRP yield ratios
```{r yield ratios, include = TRUE, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 9, fig.asp = 0.7, out.width = "100%"}
# Create dataframe to work with
rat_NO3 <- 
  som_results %>% 
  pivot_longer(cols = c(q_mm, NO3_kg_km2, SRP_kg_km2), names_to = "var", values_to = "yield") %>% 
  mutate(year = year(event_start)) %>% 
  select(site, event_start, year, SOM, clust_5cl, var, yield) %>% 
  filter((SOM == "water" & var == "q_mm") |
          (SOM == "NO3_kg_km2" & var == "NO3_kg_km2") |
          (SOM == "SRP_kg_km2" & var == "SRP_kg_km2")) %>% 
  select(-SOM) %>% 
  filter(var == "NO3_kg_km2") %>% 
  pivot_wider(names_from = var, values_from = yield)

rat_SRP <- 
  som_results %>% 
  pivot_longer(cols = c(q_mm, NO3_kg_km2, SRP_kg_km2), names_to = "var", values_to = "yield") %>% 
  mutate(year = year(event_start)) %>% 
  select(site, event_start, year, SOM, clust_5cl, var, yield) %>% 
  filter((SOM == "water" & var == "q_mm") |
          (SOM == "NO3_kg_km2" & var == "NO3_kg_km2") |
          (SOM == "SRP_kg_km2" & var == "SRP_kg_km2")) %>% 
  select(-SOM) %>% 
  filter(var == "SRP_kg_km2") %>% 
  pivot_wider(names_from = var, values_from = yield)

rat_q <- 
  som_results %>% 
  pivot_longer(cols = c(q_mm, NO3_kg_km2, SRP_kg_km2), names_to = "var", values_to = "yield") %>% 
  mutate(year = year(event_start)) %>% 
  select(site, event_start, year, SOM, clust_5cl, var, yield) %>% 
  filter((SOM == "water" & var == "q_mm") |
          (SOM == "NO3_kg_km2" & var == "NO3_kg_km2") |
          (SOM == "SRP_kg_km2" & var == "SRP_kg_km2")) %>% 
  select(-SOM) %>% 
  filter(var == "q_mm") %>% 
  pivot_wider(names_from = var, values_from = yield) %>% 
  select(-clust_5cl)

ratios <-
  full_join(rat_NO3 %>% rename(clust_5cl_NO3 = clust_5cl), rat_SRP %>% rename(clust_5cl_SRP = clust_5cl), by = c("site", "event_start", "year")) %>% 
  mutate(event_NO3_SRP = (NO3_kg_km2/14.007) / (SRP_kg_km2/30.974)) %>% 
  left_join(rat_q, by = c("site", "event_start", "year"))
rm(rat_NO3, rat_SRP, rat_q)

# HFORD
# Plot coded by clusters in NO3 5 cluster model
pl_rat_hf_NO3 <-
  ratios %>% 
  filter(site == "Hungerford") %>% 
  ggplot(aes(x = q_mm, y = event_NO3_SRP, color = factor(clust_5cl_NO3))) +
    geom_point(size = 2, stroke = 0.75, alpha = 0.8) +
    scale_color_manual(name = "Cluster",
                      values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +  
    geom_hline(yintercept = 16, linetype = "dashed", size = 0.75, color = "gray40") +
    ylab(expression(atop(Molar~ratio~of~NO[3]^-{}~":"~SRP~yield, "for"~each~event))) +
    xlab("Event water yield (mm)") +
    scale_y_continuous(limits = c(0, 1300), breaks=seq(0, 1200, 300)) +
    scale_x_continuous(limits = c(0, 80), breaks=seq(0, 80, 20)) +
    theme1 +
    theme(axis.title.y = element_text(margin=margin(0,5,0,0)),
          legend.position = "none",
          axis.title.x = element_blank()) +
  ggtitle("HFORD - colored by NO3 SOM clusters")

# Plot coded by clusters in SRP 5 cluster model
pl_rat_hf_SRP <-
  ratios %>% 
  filter(site == "Hungerford") %>% 
  ggplot(aes(x = q_mm, y = event_NO3_SRP, color = factor(clust_5cl_SRP))) +
    geom_point(size = 2, stroke = 0.75, alpha = 0.8) +
    scale_color_manual(name = "Cluster",
                      values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +  
    geom_hline(yintercept = 16, linetype = "dashed", size = 0.75, color = "gray40") +
    ylab(expression(atop(Molar~ratio~of~NO[3]^-{}~":"~SRP~yield, "for"~each~event))) +
    xlab("Event water yield (mm)") +
    scale_y_continuous(limits = c(0, 1300), breaks=seq(0, 1200, 300)) +
    scale_x_continuous(limits = c(0, 80), breaks=seq(0, 80, 20)) +
    theme1 +
    theme(legend.position = c(0.85, 0.7),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_blank()) +
  ggtitle("HFORD - colored by SRP SOM clusters")

# WADE
# Plot coded by clusters in NO3 5 cluster model
pl_rat_wd_NO3 <-
  ratios %>% 
  filter(site == "Wade") %>% 
  ggplot(aes(x = q_mm, y = event_NO3_SRP, color = factor(clust_5cl_NO3))) +
    geom_point(size = 2, stroke = 0.75, alpha = 0.8) +
    scale_color_manual(name = "Cluster",
                      values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +  
    geom_hline(yintercept = 16, linetype = "dashed", size = 0.75, color = "gray40") +
    ylab(expression(atop(Molar~ratio~of~NO[3]^-{}~":"~SRP~yield, "for"~each~event))) +
    xlab("Event water yield (mm)") +
    scale_y_continuous(limits = c(0, 1300), breaks=seq(0, 1200, 300)) +
    scale_x_continuous(limits = c(0, 80), breaks=seq(0, 80, 20)) +
    theme1 +
    theme(axis.title.x = element_text(margin=margin(5,0,0,0)),
          axis.title.y = element_text(margin=margin(0,5,0,0)),
          legend.position = "none") +
  ggtitle("WADE - colored by NO3 SOM clusters")

# Plot coded by clusters in SRP 5 cluster model
pl_rat_wd_SRP <-
  ratios %>% 
  filter(site == "Wade") %>% 
  ggplot(aes(x = q_mm, y = event_NO3_SRP, color = factor(clust_5cl_SRP))) +
    geom_point(size = 2, stroke = 0.75, alpha = 0.8) +
    scale_color_manual(name = "Cluster",
                      values = c("#999999", "#E69F00", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")) +  
    geom_hline(yintercept = 16, linetype = "dashed", size = 0.75, color = "gray40") +
    ylab(expression(atop(Molar~ratio~of~NO[3]^-{}~":"~SRP~yield, "for"~each~event))) +
    xlab("Event water yield (mm)") +
    scale_y_continuous(limits = c(0, 1300), breaks=seq(0, 1200, 300)) +
    scale_x_continuous(limits = c(0, 80), breaks=seq(0, 80, 20)) +
    theme1 +
    theme(axis.title.x = element_text(margin=margin(5,0,0,0)),
          legend.position = "none",
          axis.title.y = element_blank(),
          axis.text.y = element_blank()) +
  ggtitle("WADE - colored by SRP SOM clusters")

# Combine into one plot
(pl_rat_hf_NO3 | pl_rat_hf_SRP) / (pl_rat_wd_NO3 | pl_rat_wd_SRP)
```
Molar ratio of NO3 to SRP yield for each event. The dashed horizontal line shows the 16:1 molar N:P ratio.